---
title: "Linear_Regression"
author: "Enrique J. De La Hoz."
date: "30 de marzo de 2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Regression

Regression: Predict a numerical outcome ('dependent variable') from a set of inputs ('independent variables').

* Statistical Approach: Predicting the expected value of the outcome

* Casual Sense: Predicting a numeric outcome, rather than a discrete one.

## What is a regression?

- How many units will we sell? (**Regression**)
- Will this customer buy our product (yes/no)? (**Classification**)
- What price will the customer pay for our product? (**Regression**)

## Example: Predict Temperature from Chirp Rate

```{r echo = FALSE}
library(ggplot2)
cri<- readRDS('cricket.rds')
ggplot(cri, aes(chirps_per_sec, temperature))+ geom_point()

```


## Predict Temperature from Chirp Rate

```{r echo = FALSE}
library(ggplot2)
cri<- readRDS('cricket.rds')
ggplot(cri, aes(chirps_per_sec, temperature))+ geom_point()+  geom_smooth(method ="lm", se = FALSE) 

```

## Regression from a Machine Learning approach

* Scientific mindset: Modeling to understand the data generation process

* Engineering mindset: Modeling to predict accurately

Machine Learning: Engineering mindset

## Linear Regression

$$ y = \beta_0x_1 + \beta_1x_1 + \beta_2x_2 + ...$$

* y is linearly related to each $x_i$

* Each $x_i$ contributes additively to y

## Linear Regression in R: lm()

```{r eval= FALSE, echo=TRUE}

cmodel<- lm(temperature ~ chirps_per_sec, data = cricket)
```

* formula: temperature ~ chirps_per_sec
* dat frame: cricket

## Exercise

```{r eval= FALSE, echo=TRUE}
# Load unemployment dataset in the workspace
readRDS()

# Define a formula to express female_unemployment as a function of
# male_unemployment
fmla <- 

# Print it


# Use the formula to fit a model: unemployment_model
unemployment_model <- lm(  , data = )

# Print it

```

## Reading the results
```{r echo=FALSE, warning= FALSE}

library(broom)
library(sigr)

```

```{r eval= TRUE, echo=TRUE, message = FALSE, warning=FALSE}
unemployment<- readRDS('unemployment.rds')
unemployment_model <- lm(female_unemployment 
                         ~ male_unemployment , data = unemployment)
# Install packages broom and sigr and Call summary().
summary(unemployment_model)
```

## A better presentation of the results

```{r eval= TRUE, echo=TRUE, message = FALSE, warning=FALSE}
# Call glance() on unemployment_model to see the details
# in a tidier form
glance(unemployment_model)
```

## Another example

```{r eval= TRUE, echo=TRUE, message = FALSE, warning=FALSE}
# bloodpressure is in the workspace
bloodpressure <- readRDS('bloodpressure.rds')
summary(bloodpressure)
# Create the formula and print it
fmla <- blood_pressure ~ age + weight

# Fit the model: bloodpressure_model
bloodpressure_model <- lm(fmla, data= bloodpressure)

# Print bloodpressure_model and call summary() 
```

## Interpretation

```{r eval= TRUE, echo=TRUE, message = FALSE, warning=FALSE}
# Interpretating the summary() 
bloodpressure_model$coefficients

```
 One of the advantages of linear regression is that you can interpret the effects of each variable on the input – to a certain extent. In this case the coefficients for both age and weight are positive, which indicates that bloodpressure tends to increase as both age and weight increase.
 
 
## Visualization of the results

```{r eval= TRUE, echo=FALSE, message = FALSE, warning=FALSE}
bloodpressure$prediction <- predict(bloodpressure_model)
```

```{r eval= TRUE, echo=TRUE, message = FALSE, warning=FALSE}
ggplot(bloodpressure, aes(x=prediction,
y = blood_pressure )) + geom_point()+
geom_abline(color = "blue")
```
 
## Pros and Cons of Linear Regression

**Pros**

* Easy to fit and to apply
* Concise
* Less prone to overfitting
 
## Pros and Cons of Linear Regression

**Pros**

* Easy to fit and to apply
* Concise
* Less prone to overfitting
* **Interpretable**
```{r eval= TRUE, echo=TRUE, message = FALSE, warning=FALSE}
 lm(formula = blood_pressure ~ age + weight, data = bloodpressure)

```


## Pros and Cons of Linear Regression

**Pros**

* Easy to fit and to apply
* Concise
* Less prone to overfitting
* Interpretable

**Cons**

* Can only express linear and additive relationships

## Collinearity

* **Colinearity**: when input variables are partially correlated.

```{r eval= TRUE, echo=TRUE, message = FALSE, warning=FALSE}
 lm(formula = blood_pressure ~ age + weight, data = bloodpressure)

```

## Collinearity

* **Colinearity**: when input variables are partially correlated.

* Coefficients might change sign
```{r eval= TRUE, echo=TRUE, message = FALSE, warning=FALSE}
 lm(formula = blood_pressure ~ age + weight, data = bloodpressure)

```



* **Colinearity**: when input variables are partially correlated.

* Coefficients might change sign
    + Coefficients (or SE) too large
    + Model may be unsatble
```{r eval= TRUE, echo=TRUE, message = FALSE, warning=FALSE}
 lm(formula = blood_pressure ~ age + weight, data = bloodpressure)

```